Deciding to Disclose: Pregnancy and Alcohol Misuse

### 2014-07-09 Model.tex
Subsections

\subsection{Lexicographic Heuristic}
\label{sub:lexico}

@@

\subsubsection{Bayesian Payoff Heuristic}

@@

\begin{equation}
R_{w}(s_{w}) = \sum_{x\in \Theta} -xp(x | s_{w})
\end{equation}
\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{x\in \Theta} -xp(x | s_{w}\wedge s_{m})
\end{equation}

@@

The second Bayesian agent augments the reasoning of the simple payoff model, approximating \(u_{w}\) with a more complex function - \(f(s_{w}, \theta_{w}, \sigma_{s}, \sigma_{r})=g(s_{w}, \theta_{w}, \sigma_{s}) + h(s_{w}, \theta_{w}, \sigma_{r})\). Women maintain two sets of beliefs, one each for \(g\) and \(h\), corresponding respectively to \(p_{m}\), and the probability of referral. This leads to the risk function -

\begin{equation}
R(s_{w}) = \sum_{i\in s_{m}}\sum_{j\in \theta_{m}} -u_{w}(s_{w}, s_{m, i}, \theta_{w}, \theta_{m, j})p(j)p(i | s_{w})
\end{equation}

@@

\begin{equation}
R(s_{w}, s_{m}) = \sum_{i\in \theta_{w}} -u_{w}(s_{w}, s_{m}, \theta_{w, i}, \theta_{m})p(i | s_{w})
\end{equation}

@@

And $\alpha$, and $\beta$ are respectively the power of a gain,
and a loss. The \ac{CPT} value of outcome $x$ is $v(x)w^{+}(x)$
if $x\geq0$, and $v(x)w^{-}(x)$ otherwise. For an action the \ac{CPT}
value is the sum of the value of the prospects of that action, as
in the Bayesian risk model. The decision rule then requires the agent
to choose the action which maximises the prospect theory value.

>>>>

\subsubsection{Lexicographic Heuristic}
\label{sub:lexico}

@@

\subsubsection{Bayesian Payoff}

@@

Agents then choose $s_{i}$ to minimise $R_{i}$, which is simply - 
\begin{equation}
R_{w}(s_{w}) = \sum_{x\in \Theta} -xp(x | s_{w})
\end{equation}
\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{x\in \Theta} -xp(x | s_{w}\wedge s_{m})
\end{equation}

@@

The second Bayesian agent augments the reasoning of the simple payoff model, making the stronger assumption that the utility function is static, and known. Women maintain two sets of beliefs, one each for \(g\) and \(h\), corresponding respectively to \(p_{m}\), and the probability of referral. This leads to the risk function -

\begin{equation}
R_{w}(s_{w}) = \sum_{i\in s_{m}}\sum_{j\in \theta_{m}} -u_{w}(s_{w}, s_{m, i}, \theta_{w}, \theta_{m, j})p(j)p(i | s_{w})
\end{equation}

@@

\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{i\in \theta_{w}} -u_{w}(s_{w}, s_{m}, \theta_{w, i}, \theta_{m})p(i | s_{w})
\end{equation}

@@

And $\alpha$, and $\beta$ are respectively the power of a gain,
and a loss, and \(x=u_{i}\). The \ac{CPT} value of outcome $x$ is $v(x)w^{+}(x)$
if $x\geq0$, and $v(x)w^{-}(x)$ otherwise. For an action the \ac{CPT}
value is the sum of the value of the prospects of that action, as
in the Bayesian risk model. The decision rule then requires the agent
to choose the action which maximises the prospect theory value.
